Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-26 cvx-flats-neurips21/cvx-flats.tex
Fixing a typo

\paragraph{Q4: Variance}
One might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$, though a loss function to elicit the variance is not immediately obvious.
This property is continuous in $\simplex$, and therefore belongs in Quadrant 4.
The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
However, in Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in Section~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.

>>>>

\paragraph{Q4: Variance}
One might reasonably want to estimate the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$, though a loss function to elicit the variance is not immediately obvious.
This property is continuous in $\simplex$, and therefore belongs in Quadrant 4.
The well-known fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
However, in Appendix~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.
